---
title: "homework-3-submission"
format: docx
editor: visual
date: 5/28/25
author: Yonatan Grossman
---

Here's the link

https://github.com/Yonatan-Grossman/ENVS-193DS_homework-03.git

```{r}
library(tidyverse) #read in packages
library(here)
library(flextable)
library(janitor)
```


## Problem 1

# a.
I could make side-by-side box and whisker plots comparing the number of times I ate on days where there is and isn't a non-work stresser. I find that when I'm stressed I tend to work more and spend less time eating so I think the mediam number of times I ate when stressed will be lower, and I think the range will also be lower since the more stressed I am the overall fewer opportunities I give myself to eat.

# b.
```{r}
personal_data <- read.csv("C:/Users/16177/193 DS/ES 193DS/git/ENVS-193DS_homework_3/ENVS-193DS_homework-03/data/Personal data - Sheet1.csv") #reading in the personal data

data_clean <- personal_data |> #makes a new object called data_clean which is just the data from personal_data
  clean_names() #cleans the data


ggplot(data_clean,
       aes(x = presence_of_a_non_work_stressor_y_n,
           y = instances_of_eating,
           color = presence_of_a_non_work_stressor_y_n,
           shape = presence_of_a_non_work_stressor_y_n)) +
  geom_boxplot(show.legend = FALSE) + #boxplot
  geom_jitter(height = 0.1, width = 0.2, show.legend = FALSE) + #jitterplot
  scale_color_manual(values = c("y" = "black", "n" = "red3")) + #custom colors
  scale_shape_manual(values = c("y" = 6, "n" = 2)) + #custom shapes
  labs (x = "Presence of a non-work stresser", y = "Instances of eating") #axis labels
```

# c.
**Figure 1: Number of times I eat on days I have a non-work stresser and days I don't:**  
Comparison of number of times I eat on days I'm stressed for a reason unrelated to work (*n* = 19) and days where I'm not (*n* = 9) The boxplots represent median values, IQR, and spread of observations of number of times I ate food those days. Colors represent the location (black = stressor present, red = no stressor). The triangles represent individual observations